Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa through development of a 3D spectral numerical coastal-flow model

### 2020-07-08 thesis_chapter_1.Rmd
slight clean up on on buoyancy addition
added drag parameters section

$$weight=/deltapgV_s$$
$/deltap=p_s-p_f$

@@

>>>>

$$weight=pgV_s$$
$Density=p_s-p_f$

@@

## Drag parameters

Drag is the force an object experiences when moving in a fluid due to the rate in change of momentum [@Vogel2020]. The drag around the surface of an object due to the viscosity of the fluid is known as 'surface drag'. The drag induced by a quantity of fluid moving around the object is known as pressure drag/form drag/inertial drag. In general, large objects moving quickly tend to induce larger drag forces, however, this is not always the case. In some instances, the flow around the object changes from laminar to turbulent which ultimately reduces overall drag. (Maybe insert small section on why turbulent flow reduces overall drag on an object).

The type of flow, laminar or turbulent, is determined by fluid density (p), flow speed (U), object size (l) and fluid viscosity (v). These factors can be used to calculate the Reynolds number which is used to determine the type of flow. The expression used can be dependent on factors used such as whether the fluid is Newtonian or non-Newtonian and object shape.
